---
title: "Examples how to use `knitrContainer`"
subtitle: "(knitrContainer v`r packageVersion('knitrContainer')`)"
author: "Vilmantas Gegzna"
date: "`r Sys.Date()`"
output:
    rmarkdown::html_vignette: 
        toc: yes
        number_sections: yes
        toc_depth: 2

vignette: >
  %\VignetteIndexEntry{1 knitrContainer Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteDepends{plotly}
  %\VignetteEncoding{UTF-8}
---
```{r options1, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(collapse = TRUE,
                      comment = "#>",
                      tidy  = TRUE,
                      fig.align = 'center')
optDEF <- knitr::opts_chunk$get()
```

Introduction
=============

About `knitrContainer`
----------------------

`knitrContainer` is an [R](https://cran.r-project.org/) package designed 
to collect objects and print them in [`knitr`](http://yihui.name/knitr/) 
reports.

###  Why was it created? 

Some objects such as  `pander` tables and `plotly` plots, are not printed from
inside loop in a `knitr` report file in a regular way.`knitrContainer` solves
this problem by providing functions to get these objects printed and included 
in `HTML` files.
 
### What king of objects can be collectd and printed with `knitrContainer`?

 An object used by `knitrContainer` can be any object, that is
 includible in R list an that is printable, such as:
 
 1. text;
 2. objects printable with [`pander`](http://rapporter.github.io/pander/);
 3. [`ggplot2`](http://ggplot2.org/), [`plotly`](https://plot.ly/r/) 
 plots;
 4. etc.
 

How to install the package?
-----------------------------

From Git Hub repository:
```{r Install package, eval=FALSE}
library(devtools)
install_github("GegznaV/knitrContainer")
```


How to use `knitrContainer`? 
-----------------------------

Only 4 things should be done for basic use of `knitrContainer` package :

1. Create a container(e.g. function `knitrContainer()`);
2. Add objects to the container (use `add_as_*` family functions, e.g. function 
`add_as_is()`);
3. In a R code chunk of [`knitr`](http://yihui.name/knitr/) report file set 
option `results` to `results='asis'`;
4. Print the objects appropriately: apply
function `extract_and_print()` in the chunk which has option `results='asis'`.


### Example 1

```{r, eval = FALSE}
library(knitrContainer)
```
```{r, eval = FALSE}
container <- knitrContainer()
container <- add_as_text(container, "Text to be added.")
extract_and_print(container)
```

### Example 2

Example how to add objects using the operator `%<>%` from package
[`magrittr`](https://github.com/smbache/magrittr#compound-assignment-pipe-operations):
```{r, eval = FALSE}
container %<>% add_as_text("Text added using `%<>%` operator.")
```

It is the same as:
```{r, eval = FALSE}
container <- add_as_text(container, "Text added using `<-` operator.")
```  

Type the following code in R to learn more about operator `%<>%`:

```{r, eval = FALSE}
?`%<>%`
```


More detailed examples are presented in the following sections.

Functions for class `knitrContainer`   
===============================================

Load packages 
--------------

```{r Load main package, message = FALSE, warning = FALSE}
library(knitrContainer)

library(ggplot2)
library(plotly)
```

... and create necessary objects
```{r}
plotly_obj <- plot_ly(economics, x = date, y = uempmed, type = "scatter",
             showlegend = FALSE)

ggplot_obj <- qplot(mpg, wt, data = mtcars, colour = cyl)
```

Create a `knitrContainer` object
---------------------------------

```{r}
container <- knitrContainer()
class(container)
container
```

Attach objects to the end of the container
-------------------------------------------


```{r}
# Section headings
container <- add_as_section(container, "Plots")

# Add `plotly` objects as `htmlwidgets`
container <- add_as_section(container, "Add `plotly` as `plotly htmlwidget`", level = 2)
container <- add_as_plotly_widget(container, plotly_obj)

# Add `ggplot` objects as plotly `htmlwidgets`
container <- add_as_section(container, "Add `ggplot` as `plotly htmlwidget`", level = 2)
container <- add_as_plotly_widget(container, ggplot_obj)

# Add `ggplot` objects as `ggplot` objects
container <- add_as_section(container, "Add `ggplot` as-is", level = 2)
container <- add_as_is(container, ggplot_obj)

# If `plotly` objects are aded as-is, they might not be plotted
container <- add_as_section(container, "Attention: Not Plotted", level = 1)
container <- add_as_is(container, plotly_obj)
container <- add_as_text(container, paste("As you noticed, the last",  
      "`plotly` object was not plotted as it was added with ",  
      "`add_as_is()` and not with `add_as_plotly_widget()`"))

# --- Calculations ---
SUMMARY <- summary(mtcars[1:4])

# --- Add `pander` tables ---
container <- add_as_heading1(container, "Print SUMMARY as pander table and as text")

# Add objects, printed as `pander` tables
container <- add_as_heading2(container, "As pander table")
container <- add_as_pander(container, SUMMARY)

# Add as R output text
container <- add_as_heading2(container, "As R output text")

container <- add_as_text(container, "Highlighted as R code")
container <- add_as_r_output(container, SUMMARY)

container <- add_as_text(container, "Not highlighted")
container <- add_as_r_output(container, SUMMARY, highlight = FALSE)

container <- add_as_text(container, "With default `knitr` comments")
container <- add_as_r_output(container, SUMMARY, comment = TRUE)

container <- add_as_text(container, "With custom comments")
container <- add_as_r_output(container, SUMMARY, comment = "#$#>")

# Add as text = Add as one paragraph
container <- add_as_heading2(container, "As text/paragraph")
container <- add_as_text(container, SUMMARY)

# Add as-is
container <- add_as_heading2(container, "As is")
container <- add_as_is(container, SUMMARY)
```

Explore the container
=======================

Note, that functions `summary(container)` and `print(container)` do the same action: print
summary of the object

```{r}
print(container)

is.knitrContainer(container) 
is.knitrContainer(ggplot_obj)

as.knitrContainer(ggplot_obj) 

class(container)
```
Merge several containers.

```{r}
Join(container, container)   %>% length()
```

Convert (as is) to `knitrContainer` and merge.
```{r}
Join(container, ggplot_obj)   %>% length()
```


As function uses method "as is" to convert to `knitrContainer`, 
`plotly` objects might not be printed from the container in some situations
(e.g. from inside `for` loops using `knitr`).

```{r}
Join(ggplot_obj, plotly_obj)
```
In these situations it is better to apply function `add_as_plotly_widget` first.




Print objects from the container (`extract_and_print`)
========================================================

In section **2** there we demonstrated how to create a `knitr_nontainer`. In this
section we will demonstrate how to print all the objects from the container.

For this purpose a special function `extract_and_print` was created. As we use 
`knitr` and `R MArkdown` we recommend to use separate R code chunk to apply the
 function. It is <font color ="red"> IMPORTANT </font> to make 
 sure that R chunk, in which `extract_and_print()` is called, has option `results` 
 set to `as is` (`{r, results = 'asis'}`). Otherwise incorrect results are 
 expected.

The following text, section headings, figures etc. (except section 
"ADVANCED: ..." and "Session information") are printed from the container
using the following syntax:  

```{r, results = 'asis'}
extract_and_print(container)
```

ADVANCED: `add_as_data` and `add_as_code`
==================================================


```{r}
container2 <- knitrContainer()
# Add as data and add as code to evaluate 

# Add as data
container2 %<>% add_as_text(
    "Add `mtcars` as data (it will not be printed) and rename it to 'cars_data'.")
container2 %<>% add_as_data(mtcars, give.name = "cars_data")

# Add as code to evaluate
container2 %<>% add_as_text(
    c("Use `add_as_code` to add unquoted code which manipulates the dataset ",
      "'cars_data', e.g. prints its variable names or plots it."))
container2 %<>% add_as_code(print(names(cars_data[1:3])))
container2 %<>% add_as_code(plot(cars_data[1:3]))
```

```{r, results = 'asis'}
extract_and_print(container2)
```

Session information
===================


```{r session info}
devtools::session_info()
```
